FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-12 NewVersion/sections/Discussion.tex
Added bruno's comment on fields.

One typical non-orthogonal extension to our model could be to have fields. Having fields in OO multiple inheritance is a non-trivial issue. There has been a lot of work on it, such as C++ that uses virtual inheritance~\cite{ellis1990annotated}. The trait model simply disallows state to avoid that issue. In our language, however, we can perhaps borrow the idea of \textit{interface-based programming}~\cite{classless}, which actually models state with abstract state operations. This can be realized by extending our current model with static methods and anonymous classes from Java. To directly support fields it requires more discussions and experiments, we leave them as our future work.

>>>>

One typical non-orthogonal extension to \MIM{} could be to have fields.
The design of \MIM{} can be viewed as an extension to Java 8 with default methods which allows for unintentional method conflicts.
Like Java interfaces and traits, state is forbidden in \MIM{} since having state in OO multiple inheritance is a non-trivial issue. There has been some related work on it, such as C++ that uses virtual inheritance~\cite{ellis1990annotated}. In our model, however, we can perhaps borrow the idea of \textit{interface-based programming}~\cite{classless}, which models state with abstract state operations. This can be realized by extending our current model with static methods and anonymous classes from Java. To directly support fields it requires more discussions and experiments, we leave them as our future work.

### 2017-10-12 NewVersion/sections/Introduction.tex

\yanlin{
TODOs:
\begin{itemize}
\item UML Diagram for full solution in introduction with informal explanation
\item Move Figure 5 to end of Section 2 together with explanation
\item Improve Figure 5 with additional mbody calls
\item Improve Figure 5 with visual information that signals that in examples d) and e) then D does not type-check
\item Make names of classes more consistent in Figure 5
\item Add example (f) : A m      B m   C m   D  m  This would compile, note that if it was BArrowA m and/or CArrowA m it would also compile and D would have the same observable behaviour
\item remove S1 “Unfortunately, such an issue ...”
\item S2, should remove the discussion about JFrmae. all return type void.
\item S2, mention DrawableDeck in P2.3 is a new version of DrawableDeck before.
\item S2, “Ideally, we want that invocation to be dynamically dispatched.” --> “In FHJ, this invocation is dynamically dispatched.“. and revise the following paragraph on “we may have to copy the shuffleAndDraw code into SafeDeck, so as to be adaptive to the new draw. “.
\item S2.2 revise paragraph “Implicit and Explicit Upcasts “.
\item S2.3 (Maybe) put “Potential solutions/workarounds in existing languages” after “FHJ solution”.
\item S2.3 (Maybe) add “redraw()” method in Drawable. and add another method call similar to shuffleAndDraw()
\item Talk about Fig5 earlier. Move from S4.1 to S2.3 (a peek of ..)
%\item The keywords in code are barely distinghuishable from other code,  make them bolder/darker

\item in Figure 1, the UML diagram on the right side is not quite right, 
we want to be able to override draw from Drawable in DrawableSafeDeck, 
the override (which is *the most important point*) is not in the UML diagram.
  => Figure 1 on the right is the UML for P3 potential workaround, not for P3 FHJ, we need another UML. 
\item Submit abstract
\item Introduction to revise (by Bruno)
\item Revise overview (Yanlin and Haoyuan)
\item Section 4, 5 (Haoyuan)
\item Section 6 (Yanlin)
\item Section 7 (Yanlin and Haoyuan)
\end{itemize}
}

>>>>

\yanlin{
TODOs:
\begin{itemize}
\item UML Diagram for full solution in introduction with informal explanation
\item Move Figure 5 to end of Section 2 together with explanation
\item Improve Figure 5 with additional mbody calls
\item Improve Figure 5 with visual information that signals that in examples d) and e) then D does not type-check
\item Make names of classes more consistent in Figure 5
\item Add example (f) : A m      B m   C m   D  m  This would compile, note that if it was BArrowA m and/or CArrowA m it would also compile and D would have the same observable behaviour
\item remove S1 “Unfortunately, such an issue ...”
\item (\checkmark)S2, should remove the discussion about JFrmae. all return type void.
\item (\checkmark)S2, mention DrawableDeck in P2.3 is a new version of DrawableDeck before.
\item (\checkmark)S2, “Ideally, we want that invocation to be dynamically dispatched.” --> “In FHJ, this invocation is dynamically dispatched.“. and revise the following paragraph on “we may have to copy the shuffleAndDraw code into SafeDeck, so as to be adaptive to the new draw. “.
\item S2.2 revise paragraph “Implicit and Explicit Upcasts “.
\item S2.3 (Maybe) put “Potential solutions/workarounds in existing languages” after “FHJ solution”.
\item S2.3 (Maybe) add “redraw()” method in Drawable. and add another method call similar to shuffleAndDraw()
\item Talk about Fig5 earlier. Move from S4.1 to S2.3 (a peek of ..)
%\item The keywords in code are barely distinghuishable from other code,  make them bolder/darker

\item (\checkmark)in Figure 1, the UML diagram on the right side is not quite right, 
we want to be able to override draw from Drawable in DrawableSafeDeck, 
the override (which is *the most important point*) is not in the UML diagram.
  => Figure 1 on the right is the UML for P3 potential workaround, not for P3 FHJ, we need another UML. 
\item Submit abstract
\item Introduction to revise (by Bruno)
\item Revise overview (Yanlin and Haoyuan)
\item Section 4, 5 (Haoyuan)
\item Section 6 (Yanlin)
\item Section 7 (Yanlin and Haoyuan)
\end{itemize}
}
